From Education to Entrepreneurship

### 2014-12-09 index.Rmd
revised equation
Revised interactive chart and began building others

# Drop X column
CD$X <- NULL

R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")

@@

$Percent Perceived Opportunities = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability + 0.21Percent Fear Failure$

$+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$

@@

>>>>

CD_copy <- CD

# Drop X column
CD$X <- NULL
CD$iso2c <- NULL

R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year", options = list(state='{"showTrails":false};'))

@@

$NationalLevelAveragePercentOwningaBusiness = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability +$  
$0.21Percent Fear Failure$ $+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$

@@

# Create country vector to subset
myvars2 <- c('US','FR','DE','JP','GB')

# Subset CD
CD_subset <- subset(CD_copy, iso2c %in% myvars2)
